Deep Probabilistic Models for Camera Geo-Calibration

### 2018-07-19 chapters/introduction/introduction.tex
minor change

\subsection{Deep Neural Networks}
In recent years, deep neural networks (DNNs) rise as stars. Methods
using DNNs achieve state-of-the-art performances in
many computer vision areas (\todo{citations}). We demonstrate that
DNNs are good tools to solve partial calibration problems. 
As a next step of our study, We focus on calibrating cameras with deep
neural networks.

>>>>

\subsection{Deep Neural Networks for Geo-Calibration}
In recent years, deep neural networks (DNNs) rise as stars. Methods
using DNNs achieve state-of-the-art performances in
many computer vision areas (\todo{citations}). 
Recent work on cross-view image
geolocalization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
 has shown that convolutional neural
networks are capable of extracting features from aerial imagery
that can be matched to features extracted from ground imagery.
Vo \etal~\cite{vo2016localizing} extend this line of work,
demonstrating improved geolocalization performance by applying an
auxiliary loss function to regress the ground-level camera orientation
with respect to the aerial image.
